PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-08-30 txt/manuscript_short.tex
Add original expansion of state-of-the-art section written by P. Lewandowska

Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
group) and tests how much the output distribution obtained from the device running these circuits
differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
inverses (which should yield the identity circuit) and run those concatenated circuits on the
device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
\cite{forest-benchmarking}.

>>>>

Another possible approach to benchmarking quantum computers is randomized benchmarking. In this
approach, one samples circuits to be run from some predefined set of gates (e.g. from the Clifford
group) and tests how much the output distribution obtained from the device running these circuits
differs from the ideal one. It is also common to concatenate randomly chosen circuits with their
inverses (which should yield the identity circuit) and run those concatenated circuits on the
device. Libraries implementing this approach include Qiskit \cite{qiskit-randomized} or PyQuil
\cite{forest-benchmarking}. Another, equally popular benchmarking method is
quantum tomography. Such
Python package using this approach for benchmarking NISQ devices can be found in \cite{tomography}. The theory behind the software could be found in \cite{bantysh2021quantum}.

Different authors, Patel et al. \cite{patel2020experimental}  evaluated
several IBM-Q machines using seven benchmarks regarding the
error and execution time. Roughly the same time, LaRose \cite{larose2019overview} extended benchmarking methods  comparing up to
four widely used QC programming environments i.e. PyQuil, Qiskit, Project and QDK/Q$\#$
in terms of library support, hardware, compiler and simulator performance.

QASMBench \cite{li2023qasmbench} is  one of the first benchmark suite aiming at evaluating NISQ
devices using quantum applications from a broad range of domains. Their  approach  is mainly based on fidelity estimation. They analyze and compare the fidelity of executions
among the IBM-Q machines, the IonQ QPU and the Rigetti Aspen M-1 system.
